Simulations log

### 2020-04-13 simulation_study/hpoptimization/README.Rmd
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

---
title: "log hyperparameter optimization"
output: html_notebook
---

Per day, all commands sent to surfsara

After a command is sent, save that todo checklist file!

```{r}
hpsets <- readRDS("../R/01_hyperparameter_sets.RDS")

d <- colnames(hpsets)
condition <- rownames(hpsets)
classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
names(classifier) <- c("B", "R", "S", "L", "N")
```

# one on one optimization

## classifiers 
BCTD on all datasets
```{r}
# BCTD
script <- noquote(sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d %s -r 23", d))
write.table(script, file = "scripts/one/nb_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
# job names
names(script) <- c("7846991", "7846993", "7846994", "7846997", "7846998", "7846999")
```

```{r}
# check off to do list. 
hpsets["NCTD", , ] <- 9 # impossible model
hpsets["BCTD", , "one"] <- 1 # finish nb one-one-one simulations
```

The other 3 classifiers 
```{r}
cons <- expand.grid(c = classifier[2:4], d = d, stringsAsFactors = FALSE)
# all models
class1 <- sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$c, cons$d)
write.table(class1, file = "scripts/one/three_classifiers.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# job names
names(class1) <- c(7847065,7847066,7847067,7847068,7847069, 7847070, 7847071,7847072, 7847074,7847075, 7847076, 7847077,7847078,7847079,7847080,7847081, 7847082,7847084)

hpsets[condition[2:4], , "one"] <- 1
```

## now with doc2vec feature extraction 
```{r}
cons <- expand.grid(c = classifier[2:5], d = d, stringsAsFactors = FALSE)

# a test run first maybe
# NCDD
noquote("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e doc2vec -q max -d ace -r 23") # 7847109
# todo list
hpsets[condition[6], , ] <- 9 # multinomial nb cannot deal with doc2vec (negative values!!)
```

```{r}
# then all classifier * dataset combinations. 
t <- rep(c("12", "42", "42", "5-00"), length(d))
d2v1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", t, cons$c, cons$d)
# one test of doc2vec 
write.table(d2v1, file = "scripts/one/doc2vec.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2v1) <- c("7854137", "7854187", "7854188", "7854208", 
                 "7854189", "7854190", "7854191", "7854209", 
                 "7854192", "7854193", "7854194", "7854210", 
                 "7854195", "7854196", "7854197", "7854211", 
                 "7854198", "7854199", "7854200", "7854212", 
                 "7854201", "7854202", "7854203", "7854213")

hpsets[condition[7:10], ,"one"] <- 1
```

# n
```{r}
t <- c("12:00:00", "24:00:00", "48:00:00", "24:00:00")
# optimize hyperparams over all datasets
allc <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e tfidf -q max -r 23", t, classifier[1:4])
write.table(allc, file = "scripts/n/fourclassifiers.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# later for more than 12 hours. 
names(allc) <- c("7848203", "7848204", "7848205", "7848206")

hpsets[condition[1:4], , "all"] <- 1
```

## doc2vec models 
```{r}
t <- rep(c("42", "42", "42", "5-00"))
cons <- expand.grid(c = classifier[2:5], stringsAsFactors = FALSE)

d2vall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -r 23", t, cons$c)

write.table(d2vall, file = "scripts/n/doc2vec.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2vall) <- c("7854227",  "7854228", "7854229", "7854230")

hpsets[condition[7:10], ,"all"] <- 1

@@

# n-1

--- 
# Visual inspection 30-03-2020

## classifiers
```{bash, eval = FALSE}
# script to show all lisa.err files to see if processes done yes/no
.catlisaerr.sh
```
- svm 
  - ace (3x) 3 times the time. 
  - nudging 7x
  - ptsd 7x 
  - software 3x (of 4)
  - virus 5x
  - wilson 3x
    - all 10x
- rf 
  - software 2x 
  - all 3x
- rest is fine, over 1000 runs and seems not to improve much. 
```{r}
hpsets[condition[c(1,4)], , c("one", "all")] <- 2
hpsets[condition[c(2,3)],  d[c(1:2, 5:6)], "one"] <- 2
```

Sent in around 13 pm (30.03.2020)
```{r}
# svm extra time 
cons <- expand.grid(c = classifier[3], stringsAsFactors = FALSE, d= d)
cons$t <- c("36", rep("84", 2), "48", "60", "36")
extrasvm1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
names(extrasvm1) <- c("7867379","7867380", "7867382", "7867383", "7867384", "7867387")

cons <- expand.grid(c=classifier[2], stringsAsFactors = FALSE, d=d[3:4])

cons$t <- c("06", "24")

extrarf1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
names(extrarf1) <- c("7867388", "7867389")

# later check rf - ptsd - one
hpsets[condition[2], d[3], "one"] <- 2

cons <- data.frame(c = classifier[2:3], t = c("5-00", "5-00"))
extraall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -r 23", cons$t, cons$c)
names(extraall) <- c("7867412", "7873506")

# save scripts for reproducibility 
write.table(c(extrasvm1, extrarf1), file = "scripts/one/extratime_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
write.table(extraall, file = "scripts/n/extratime_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
```

## doc2vec 
```{bash, eval = FALSE}
# bash script to print all hyperopt results. 
./show.sh
```

- nn-2-layer - try again with -r 11.  (for all datasets still doesn't work )

```{r}
# redo nn-2-layer with doc2vec. 
#./cart_hyper_run.py hyper-active -t 01:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 11 7867616 test for an hour 
hpsets[condition[10], , "one"] <- 8 # error
cons <- expand.grid(c = classifier[5], stringsAsFactors = FALSE, d=d)
cons$t <- "5-00:00:00"
nn2dv1 <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e doc2vec -q max -d %s -r 11", cons$t, cons$c, cons$d)
write.table(nn2dv1, file = "scripts/one/nn2d2v.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(nn2dv1) <- c("7872280", "7872281", "7872282", "7872283", "7872284", "7872285")
hpsets[condition[10], , "one"] <- 1 # sent in again
# this can be turnt of afer 52 hours. (thursday morning) 02.04

nn2d2vall <- c("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m nn-2-layer -b double -e doc2vec -q max -r 4")
write.table(nn2d2vall, file = "scripts/n/nn2d2v.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(nn2d2vall) <- "7873511"
```

- rf is done 
  - ace 3x? 
  - nudging 2x 
  - ptsd 6x
  - software 10 x
  - virus 1.5 x 
  - wilson 1x

```{r}
# redo random forest d2v
t <- rep(c("36", "24", "72", "5-00", "18", "12"))
x_d2v_rf <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m rf -b double -e doc2vec -q max -d %s -r 23", t, d)
# one test of doc2vec 
write.table(x_d2v_rf, file = "scripts/one/x_d3v_rf.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(x_d2v_rf) <- c("7867607", "7867608", "7867609", "7867610", "7867611", "7867612")
```

# asreview create-config

# export config files 
(from all files in output :) )

```{r}
d4 <- c(paste(d[1:5], collapse=","), 
        paste(d[2:6], collapse=","), 
        paste(d[c(3:6,1)], collapse = ","), 
        paste(d[c(4:6, 1:2)], collapse=","),
        paste(d[c(5:6, 1:3)], collapse = ","),
        paste(d[c(6, 1:4)], collapse = ","))
cons <- expand.grid(c = classifier, d = d4, f=c("tfidf", "doc2vec"), stringsAsFactors = FALSE)
cons <- cons[!(cons$c == "nb" & cons$f == "doc2vec"), ]
cons$r <- ifelse(cons$c == "nn-2-layer", "11", "23")
cons$t <- ifelse(cons$c == "nb", "12", "5-00")
# all models
n_1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e %s -q max -d %s -r %s", cons$t, cons$c, cons$f, cons$d, cons$r)
write.table(n_1, file = "scripts/n-1/all_models.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# job names
names(n_1) <- c("7873344", "7873345", "7873346", "7873347", "7873348",
                "7873360", "7873361", "7873363", "7873364", "7873365",
                "7873378", "7873379", "7873381", "7873382", "7873383",
                "7873392", "7873393", "7873394", "7873396",
                "7873396",
                "7873397", "7873398", "7873399", "7873400", "7873401",
                "7873407", "7873408", "7873409", "7873411", "7873413",
                "7873425", "7873427", "7873429", "7873431", "7873433",
                "7873446", "7873448", "7873450", "7873453", 
                "7873455",
                "7873460", "7873461", "7873462", "7873463",
                "7873464",
                "7873466", "7873467", "7873468", "7873469", "7873470", 
                "7873471", "7873472", "7873473", "7873474")

hpsets[c(1:5, 6:10),,"four"] <- 1
```

31.03.2020
### all 
all SCDD, LCDD RCDD, resend for 5 days 
```{r}
# more time for doc2vec all datasets - svm + logistic 
d2vall
cons <- expand.grid(c = classifier[2:4], stringsAsFactors = FALSE)
d2vall_x <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e doc2vec -q max -r 23", cons$c)
write.table(d2vall_x, file = "scripts/n/d2v_all_x.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2vall_x) <- c("7873497", "7873499","7873500")
```

try nn2 with tfidf -r 11

checkout nn 2 layer tfidf

### one
one LCDD, for 2x the time 
one SCDD for 1x the time 
```{r}
cons <- expand.grid(c = classifier[3:4], d = d, stringsAsFactors = FALSE)
cons$t <- ifelse(cons$c=="logistic", "96", "48")
d2v1_x <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", cons$t, cons$c, cons$d)
write.table(d2v1_x, file = "scripts/one/d2vone_x.txt", sep="\t", quote = FALSE, row.names = FALSE)

names(d2v1_x) <- c("7877706", "7877707", "7877708", "7877709", "7877710",
                   "7877711", "7877712", "7877713", "7877714", "7877715", "7877716", 
                   "7877717")
```

```{r}
hpsets[condition[2], d[4] , "one"] <- 2
```

01.04
nn-2-layer retry r-1 
```{r}
cons <- expand.grid(c = classifier[5], fe = c("tfidf", "doc2vec"), d = d, stringsAsFactors = FALSE)

nn_test <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 2", cons$c, cons$fe, cons$d)
write.table(nn_test, file = "scripts/one/nn_test.txt", sep="\t", quote = FALSE, row.names = FALSE)

names(nn_test) <- c("7891389", "7891390", "7891391", "7891392", "7891393", "7891394", "7891395", "7891396", "7891402", "7891407", "7891408", "7891411")
# ./cart_hyper_run_asrnn.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d wilson -r 2 # 7886988, 
#./cart_hyper_run.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 2 # 7883466
# ssh tcn560
# top 
```

```{r}
# cancel all logistic 4-1 sets 
#  7873347, 7873448, 7873460, 7873464, 7873469, 7873473
hpsets["LCTD", , "four"] <- 2
```

03.04.2020
```{r}
# svm d2v one are done! 
hpsets["SCDD",, "one"] <- 2
```

>>>>

---
title: "Hyperparamter optimization"
output:   
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(ggplot2)
library(knitr)

php <- function(data){
  data %>%
    filter(param %in% numericalvars) %>%
    mutate(value = as.numeric(value)) %>% 
    ggplot(aes(x = value, y = "", color = group)) +
    geom_jitter(height = 0.2) +
    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
    geom_vline(aes(xintercept = lb), color = "grey") +
    geom_vline(aes(xintercept = ub), color = "grey") 
}

php_c <- function(data){
  data %>%
    filter(param %in% categoricalvars) %>%
    mutate(value = as.factor(value)) %>% 
    ggplot(aes(x = value, color = group, fill = group, group = group)) +
    geom_bar(position="dodge") +
    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")
}
```

```{r, figure.heigth = 12}
hpsets <- readRDS("config/hpresults.RDS")
numericalvars <- c("balance_param.a", "balance_param.alpha", "balance_param.b", "model_param.alpha", "model_param.c", "model_param.class_weight", "feature_param.vector_size", "feature_param.epochs", "model_param.n_estimators")
categoricalvars <-c("feature_param.ngram_max", "feature_param.split_ta", "feature_param.use_keywords", "model_param.gamma", "feature_param.dbow_words", "feature_param.dm", "feature_param.dm_concat", "feature_param.min_count", "feature_param.window", "model_param.max_features") 
```

```{r}
library(tidyverse)
trials <- read_csv("trials/trials.csv")
```

```{r}
lossp <- function(trials, sort = TRUE){
  if(sort){
  p <-  trials %>%
    ggplot(aes(x = nrow(trials):1, y = loss))
  } else {
  p <- trials %>%
    ggplot(aes(x = trial, y = loss))
  }
  p + geom_line()

}
```

# Naive Bayes + TF-IDF

## Loss plots
```{r}

@@

## Hyperparameter values
```{r NB_TFIDF}
php(hpsets$nb_tfidf) + 
  labs(title = "Hyperparameters Naive Bayes + TF-IDF")

# plot feature_param.ngram_max
hpsets$nb_tfidf %>%
  php_c()

# SVM + TF-IDF 
```{r SVM_TFIDF, eval = FALSE}
hpsets$svm_tfidf %>%
  php() +
  labs(title = "Hyperparameters SVM + TF-IDF")

hpsets$svm_tfidf %>%
  php_c() 
```

```{r LR_TFIDF}
php(hpsets$lr_tfidf) + 
  labs(title = "Hyperparameters Logistic Regression + TF-IDF")

hpsets$lr_tfidf %>%
  php_c()
```

```{r LR_D2V, eval}
php(hpsets$lr_d2v) + 
  labs(title = "Hyperparameters Logistic Regression + Doc2Vec")

hpsets$lr_d2v %>%
  php_c()
```

```{r}
php(hpsets$rf_tfidf) + 
  labs(title = "Hyperparameters Random Forest + TF-IDF")

hpsets$rf_tfidf %>%
  php_c()
```

```{r}
php(hpsets$rf_d2v) + 
  labs(title = "Hyperparameters Random Forest + Doc2Vec")

hpsets$rf_d2v %>%
  php_c()
```

statistics for random forest + tf-idf
```{r}
hpsets$rf_tfidf %>%
   group_by(param, group) %>%
    summarise(variance = var(value), 
              sd = sd(value),
              min = min(value), 
              mean = mean(value),
              median = median(value),
              max = max(value)) %>%
  kable("markdown")
```

### 2020-04-13 simulation_study/simulation/README.Rmd
fix bugC-parameter LCDD config files
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lcdt.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c("7883218", "7883219", "7883220", "7883221", "7883223", "7883224",
                     "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")
```

@@

# run simulations 
scdd <- createLines(condition[8], d, "one")
write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(scdd) <- c("7893237", "7893241", "7893243", "7893244", "7893246", "7893247")
sims[condition[8], d, "one"] <- 2 # simulations are running

# transfer to harddrive 
transfer("one", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

all - LCTD hyperparameters 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github

# run simulations 
lctd_n <- createLines(condition[4], d, "all")
write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(lctd_n) <- c()
#sims[condition[4], d, "all"] <- 2 # simulations are running

# transfer to harddrive 
transfer("n", condition[4])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

>>>>

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c(rep("0", 6), "7949940", "7949952", "7949953", "7949954", "7949956", "7949959")
```

@@

# run simulations 
scdd <- createLines(condition[8], d, "one")
write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
           row.names = FALSE)
 names(scdd) <- c("7950186", "7950187", "7950188", "7950189", "7950190", "7950191")
 sims[condition[8], d, "one"] <- 2 # simulations are running 
```

```{r}
 sctd <- createLines(condition[3], d, "one")
 write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(sctd) <- c("7950483", "7950484", "7950485", "7950487", "7950489", "7950490")
sims[condition[3], d, "one"] <- 2 # simulations are running
```

```{r}
rcdd <- createLines(condition[7], d, "one")
write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(rcdd) <- c("7950491", "7950493", "7950495", "7950496", "7950497", "7950499")
sims[condition[7], d, "one"] <- 2 # simulations are running
```

```{r}
lcdd <- createLines(condition[9], d, "one")
write.table(lcdd, file = "scripts/one/lcdd.txt", sep = "\t", quote = FALSE, row.names = FALSE)
names(lcdd) <- c("7965136", "7965141", "7965143", "7965145", "7965146", "7965147")
sims[condition[9], d, "one"] <- 2 # simulations are running
```

10.04.2020

```{r}
# LCTD and SCDD both failedsimulations both failed? 
# ran again 
# transfer to harddrive
transfer("one", condition[c(4,7:9)])
# sctd is not finished yet! 
sims[condition[4],,"one"] <- 3 # output is on harddrive

# sims[condition[7],,"one"] <- 3 # output is on harddrive 
# sims[condition[8],,"one"] <- 3 # output is on harddrive 
# too little space for 9, so run again

sims[condition[9],,"one"] <- 3 # output is on harddrive 
# but ace wasn't finished yet!

Repeat all failed simulations

```{r}
# run again 
# transfer to harddrive 
transfer("one", condition[8])

#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

### all 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github

```{r}
# run simulations 
# lctd_n <- createLines(condition[4], d, "all")
# write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
#             row.names = FALSE)
# names(lctd_n) <- c()
# #sims[condition[4], d, "all"] <- 2 # simulations are running 
# 
# # transfer to harddrive 
# transfer("n", condition[4])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```
